\documentclass[12pt]{article}

\usepackage{palatino} 
\usepackage{enumerate}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=2.5cm, bottom=1.5cm, a4paper]{geometry}

\newcommand{\txscbf}[1]{\textsc{\textbf{#1}}}

\title{\textbf{Scientifically Advanced Writing Skills}}
\author{Dai Wenxun \\ Xidian University \\ xfeynman@gmail.com}
\date{Last Updated on \today}

\begin{document}
\maketitle

\centering \txscbf{How Europe has mishandled the pandemic}
\begin{itemize}
    \item The European Union \textbf{is} rich, \textit{scientifically advanced} and \textbf{endowed with} excellent health-care and welfare systems and a political consensus \textbf{tilted strongly towards} looking after its citizens.
    \item However, it is \textbf{in the grip of} a vicious surge \textbf{fuelled by} a deadly variant.
    \item \textbf{Part of Europe’s problem is} demography. EU populations are old by global standards, making them more susceptible to the disease. \textbf{Other less well understood factors}, such as crowded cities, may also make Europeans vulnerable.
    \item When things are at their worst, those words \textbf{are seized on} to suggest the EU will \textbf{snatch victory from the jaws of defeat}.
    \item But, \textit{inexorably}, the EU is falling behind China and America because it fails to \textbf{grapple competently with} each successive crisis.
\end{itemize}

\vspace{2ex}
\centering \txscbf{China wants to make its Christians more Chinese}
\begin{itemize}
    \item Such was the scorn for those who \textbf{embraced the faith} that, long before the Communist Party seized power in 1949, people used to say, “One more Christian, one fewer Chinese.”
    \item These principles should \textbf{feature more prominently in} their training.
    \item For now, social media \textbf{remain awash with} Christian material.
\end{itemize}

\vspace{2ex}
\centering \txscbf{China’s rulers want more control of big tech}
\begin{itemize}
    \item Because of the breadth of services that many Chinese “super-apps” encompass they have \textbf{a richer picture of} users.
    \item But that \textbf{is hardly an insurmountable obstacle for} an authoritarian regime.
\end{itemize}

\vspace{2ex}
\centering \txscbf{India is struggling with a catastrophic second wave}
\begin{itemize}
    \item Addressing university students in late January, Narendra Modi, the prime minister, \textbf{drew parallels between} cricketing glory \textbf{and} his government’s war on covid, noting that both situations presented challenges that required a positive mindset.
    \item The surging caseload has \textbf{scattered many dominoes}, including trust in Mr Modi’s government. 
\end{itemize}

\vspace{2ex}
\centering \txscbf{Serving up hope}
\begin{itemize}
    \item Food allergies are a growing, \textit{potentially} life-threatening problem. The good news is we can \textbf{turn} this \textbf{around}(e.g. He \textbf{turned around} the \textit{deteriorating situation}.).
    \item Thankfully, we are building up the armoury needed to reverse this trend so that, one day, such potentially deadly reactions \textbf{become a thing of the past}.
    \item The most common types of food allergies are \textbf{triggered} by antibodies that we make called immunoglobulinE or IgE.
    \item These antibodies were discovered in the mid-1960s and \textbf{kick-started an era of} allergy research still going strong today.
    \item The early findings have \textit{spawned} thousands of studies that \textbf{paint an intricate picture of} how allergies work, suggesting ways in which we can prevent and treat them.
    \item This causes symptoms \textbf{ranging from} itchiness and sneezes \textbf{to} wheezing and anaphylactic shock. The result can be \textbf{anything from} a mild inconvenience \textbf{to} death.
    \item Significant advances have been made in ..., but many fundamental questions have \textbf{yet to} be answered.
    \item However, other approaches are \textbf{taking shape}.
    \item \textbf{We are on the threshold of a new era.}
    \item Many of us around the world are aiming to \textit{forge} a new era, one \textit{in which} this scourge is a thing of the past.
\end{itemize}

\vspace{2ex}
\centering \txscbf{China wants the world to know that resistance to its rise is futile}
\begin{itemize}
    \item Leaders of China and America \textbf{\textit{share}} an obsession: the notion \textbf{that} a large enough coalition of Western democracies might \textbf{have the heft to} confront a rising China about its authoritarian, state-capitalist ways, and \textbf{\textit{demand}} that it follow a new trajectory, one \textit{that} does less damage to norms and universal values \textit{that} have governed the rich world since 1945.
\end{itemize}

\vspace{2ex}
\centering \txscbf{Only negotiations can bring lasting peace to Israel and Palestine}
\begin{itemize}
    \item Jerusalem \textbf{epitomises} the problem.
\end{itemize}

\vspace{2ex}
\centering \txscbf{China is in danger of being humiliated at the winter Olympics}
\begin{itemize}
    \item At one point he tells a group of young ice-hockey players that \textbf{China’s “hopes are pinned on your generation”}.
\end{itemize}

\vspace{2ex}
\centering \txscbf{Race in America}
\begin{itemize}
    \item When George Floyd was killed by Derek Chauvin a year ago, the sense of injustice \textbf{was tinged with} despair. 
    \item Instead, the country can \textbf{make common cause} to shrink enduring racial disparities while helping all Americans leave injustices behind. 
\end{itemize}

\vspace{2ex}
\centering \txscbf{The new geopolitics of global business}
\begin{itemize}
    \item Instead the bright hope was in Europe, where a new single currency promised to \textbf{catalyse} a giant business-friendly integrated market.
\end{itemize}

\end{document}